---
title: "EDA"
output: html_document
---
## New Variables:
1. host_exp_years: years since becoming a host

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r load}
library(readr)
library(dplyr)
train_x <- read_csv("airbnb_train_x.csv")
train_y <- read_csv("airbnb_train_y.csv")
test_x <- read_csv("airbnb_test_x.csv")
my_train_x<- train_x[, 29:42]
```

## see all the variables

```{r pressure, echo=FALSE}
train_x %>% colnames() 
```

```{r}
train.cor <- cor(as.matrix(train_x[, c(3, 5, 6)]))
train.cor
```

```{r}
library(funModeling) 
library(tidyverse) 
library(Hmisc)
status(my_train_x)
```

```{r}
glimpse(my_train_x)
```

## host_listings_count
how many listings the host has right now
```{r host_listings_count, echo=FALSE}
my_train_x[, 1] %>% summary()

boxplot(my_train_x[, 1])


```

```{r}
host_listings_count_freq<- as.data.frame(table(unlist(my_train_x[, 1])))
plot(host_listings_count_freq$Var1, host_listings_count_freq$Freq)
# skewed to left, median is 1, has 151 NAs
```

## host_location
```{r host_location}
my_train_x[, 2]

```

## host_name 
```{r host_location, echo=FALSE}
m3 <- as.data.frame(my_train_x[, 3])

#number of na is 147
is.na(m3) %>% table()

temp<- filter(m3, is.na(m3)==FALSE)

#convert all elements to lowercase
for (i in 1: nrow(temp[1])){
  temp[i, 1] <- tolower(temp[i, 1])
}

temp$couple <- as.integer(grepl(pattern = " and |\\+|\\&", x = temp$host_name))
sum(temp$couple)
# 7148 couple hosts
```

##  host_neighbourhood 
```{r host_location, echo=FALSE}
m4<- my_train_x[, 4]
describe(m4)

# a lot of missing values


```

## host_response_rate
```{r host_location, echo=FALSE}
m5 <- my_train_x[, 5]



# coerce wrong inputs such as "house", "Apartment" as NA
m5 <- as.character(unlist(m5))
m5 <- (as.numeric(sub("%", "", m5))/100) #remove percent sign


freq(m5)
describe(m5)
#very skewed, most hosts respond quickly
```


## host_response_time 
```{r host_location, echo=FALSE}
freq(my_train_x[, 6])

# One-hot encoded
m6 <- my_train_x[, 6]%>%mutate( 
  		# Create 
  		an_hr = ifelse(host_response_time  == "within an hour", 1, 0),
  		few_hr = ifelse(host_response_time  == "within a few hours", 1, 0),
  		a_day = ifelse(host_response_time  == "within a day", 1, 0),
  		few_days = ifelse(host_response_time  == "within a few days", 1, 0))

# don't know what f means
```

## host_since
```{r host_location, echo=FALSE}
m7 <- my_train_x[, 7]
m7 <- as.Date(m7$host_since)
plot(as.data.frame(train_x[35]), as.data.frame(train_y[3]))

x<-as.data.frame(train_x[35])
y<- as.data.frame(train_y[2])

df<- cbind(x,y)
ggplot(data = df, aes(x = df$host_since, y = df$review_scores_rating))+
  geom_line(color = "#00AFBB", size = 0.4)


# Create new variable of years since first becoming a host
today <- as.Date("2020-04-04")
host_exp_years<- difftime(today, m7)/365

```

## host_total_listings_count
```{r host_location, echo=FALSE}
my_train_x[, 8]

```

## host_response_rate
```{r host_location, echo=FALSE}
my_train_x[, 9]

```

## host_response_rate
```{r host_location, echo=FALSE}
my_train_x[, 10]

```

## host_response_rate
```{r host_location, echo=FALSE}
my_train_x[, 11]
```

## host_response_rate
```{r host_location, echo=FALSE}
my_train_x[, 12]
```

## host_response_rate
```{r host_location, echo=FALSE}
my_train_x[, 13]
```

## host_response_rate
```{r host_location, echo=FALSE}
my_train_x[, 14]
```
