---
title: "R Notebook"
output:
  html_notebook: default
  pdf_document:
    latex_engine: xelatex
always_allow_html: yes
---

```{r setup, include=FALSE}

# This chunk shows/hides the code in your final report. When echo = TRUE, the code
# is shown in the report. When echo = FALSE, the code is hidden from the final report.
# We would like to see your code, so please leave the setting as is during the course.
# This chunk will not show up in your reports, so you can safely ignore its existence.

knitr::opts_chunk$set(echo = TRUE)

```


The following is your first chunk to start with. Remember, you can add chunks using the menu
above (Insert -> R) or using the keyboard shortcut Ctrl+Alt+I. A good practice is to use
different code chunks to answer different questions. You can delete this comment if you like.

Other useful keyboard shortcuts include Alt- for the assignment operator, and Ctrl+Shift+M
for the pipe operator. You can delete these reminders if you don't want them in your report.


```{r}
setwd("C:/") #Don't forget to set your working directory before you start!

library("tidyverse")
library("plotly")
library("skimr")
library('mice')

library("fpp3")
library("plotly")
library("skimr")
library("lubridate")
```
```{r}
air1Chicago<- read_csv("Chicagodata.csv")

head(air1Chicago)
```


```{r}
air1Chicago$security_deposit<- as.numeric(gsub("\\$", "", air1Chicago$security_deposit))
air1Chicago$price <- as.numeric(gsub("\\$", "", air1Chicago$price))
air1Chicago$cleaning_fee <- as.numeric(gsub("[$]", "", air1Chicago$cleaning_fee))
air1Chicago$extra_people <- as.numeric(gsub("\\$", "", air1Chicago$extra_people))
air1Chicago$bathrooms <- as.numeric(air1Chicago$bathrooms)
air1Chicago$beds <- as.numeric(air1Chicago$beds)
air1Chicago$accomodates <- as.numeric(air1Chicago$accommodates)
air1Chicago$availability_30 <- as.numeric(air1Chicago$availability_30)
air1Chicago$availability_60 <- as.numeric(air1Chicago$availability_60)
air1Chicago$availability_90 <- as.numeric(air1Chicago$availability_90)
air1Chicago$availability_365 <- as.numeric(air1Chicago$availability_365)
air1Chicago$guests_included <- as.numeric(air1Chicago$guests_included)
air1Chicago$host_response_rate <- as.numeric(gsub("\\%", '', air1Chicago$host_response_rate))
```


```{r}

tempChicago<- air1Chicago%>%
  select(review_scores_rating, id, review_scores_value,security_deposit,price,beds,bedrooms,host_response_rate,extra_people,cleaning_fee,review_scores_rating,accommodates,availability_30,availability_90,availability_365)

head(tempChicago)
```

```{r}
tempData <- mice(tempChicago,m=3,maxit=50,meth='pmm',seed=500)
#summary(tempData)

```

```{r}
completedData <- complete(tempData,1)
```





